Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/ordering.tex
Minor fixes

Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

@@

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
We use an inverse proof and assume $\wrks{S'}$.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that, as a subsequence,
do not form a construction or destruction pair.
However, this contradicts \cref{simple_distant_pairs}
which means that no such subsequence exists.
\end{proof}

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = \{T \whr T\equiv S \wedge T \mbox{~is simple} \}. \]
\end{mylem}

% TODO APPENDIX
\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T$, $T\equiv S$, then $T\in\orderset{S}$.
We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv \wrksx{S}$.

@@

It can be shown in the same way
that the case when the $n_\indx$ nodes ascend the tree,
that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction.
In this case we find that all commands are destruction commands,
and so $[y_\indx]\neq[\vald]$, while in a subsequence of $T$ for a given $\indx$,
$[y_\indx]=[\vald]$ must be true by the definition of $\ordersetsign$.
\end{proof}

>>>>

Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks} when there are no assertion commands.

@@

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
We use an inverse proof and assume $\wrksx{S'}$.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that, as a subsequence,
do not form a construction or destruction pair.
However, this contradicts \cref{simple_distant_pairs}
which means that no such subsequence exists.
\end{proof}

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = \{T \whr T\equiv S \:\wedge\: T \mbox{~is simple} \}. \]
\end{mylem}

\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T$, $T\equiv S$, then $T\in\orderset{S}$.
We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv \wrksx{S}$.

@@

It can be shown in the same way
that the case when the $n_\indx$ nodes ascend the tree,
that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction.
In this case we find that all commands are destruction commands,
and so $[y_\indx]\neq[\vald]$, while in a subsequence of $T$ for a given $\indx$,
$[y_\indx]=[\vald]$ must be true by definition of $\ordersetsign$.
\end{proof}
